\documentclass[useAMS]{mn2e}
%To produce a PDF file with hyperlinks, uncomment the following lines
%\usepackage[pdftex,pdfpagemode={UseOutlines},bookmarks,bookmarksopen,
%colorlinks,linkcolor={blue},citecolor={green},urlcolor={red}]{hyperref}

%Original file 1999 October 18
%Modified 2000 January 19

\begin{document}
\title{New features in the \textit{Monthly Notices} \LaTeXe\ class file}
\date{2001 February 06}
\pubyear{2001} \volume{000} \pagerange{1} \onecolumn

\maketitle \label{firstpage}
 \nokeywords

The MNRAS \LaTeXe\ class file is implemented by placing the
command\\
 \verb"\documentclass["\textit{options}\verb"]{mn2e}"\\
at the start of the document.

The various \verb"option" commands listed in the \textit{Monthly
Notices}\ \LaTeX\ style guide for authors\nocite{209guide} can
still be used. The following additional options
exist.\label{dcolumn}

\begin{enumerate}
\item \verb"useAMS" -- this enables the production of upright Greek
characters $\upi$, $\umu$ and $\upartial$ (\verb"$\upi$",
\verb"$\umu$" and \verb"$\upartial$") and slanted $\leq$ and
$\geq$ (\verb"$\leq$" and \verb"$\geq$"). Characters $\upi$,
$\umu$ and $\upartial$ appear upright only on systems that have
the Euler roman fonts (\verb"eurm"\textit{xx}); characters $\leq$
and $\geq$ appear slanted only on systems that have the AMS
series A fonts (\verb"msam"\textit{xx}). On systems that do not
have these fonts, the standard forms of the characters appear in
the printout; however, they should be correct in the final typeset
paper if the correct \LaTeX\ commands have been used.

\item \verb"usedcolumn" -- this uses the package file \verb"dcolumn.sty"
to define two new types of column alignment for use in tables. If
the \verb"usedcolumn" option has been specified then, within a
table,
 \verb"d{"\textit{x}\verb"}" can be used to produce a
`flush right' decimal-aligned column with \textit{x} decimal
places and
 \verb"." can be used to provide a decimal-aligned column centred
 on the decimal point (the number of decimal places does not need
 to be specified for this column type). Note that the standard \LaTeX\
 `tools' packages \verb"dcolumn.sty" and \verb"array.sty" are
 required in order to use the \verb"usedcolumn" option.

\item \verb"usenatbib" -- this uses Patrick Daly's \verb"natbib.sty"
package for cross-referencing. If the \verb"usenatbib" option is
specified, citations in the text should be in one of the following
forms (or one of the additional forms documented within
\verb"natbib.sty" itself).

  \begin{itemize}
  \item \verb"\citet{"\textit{key}\verb"}" produces text citations,
  e.g. Jones et al. (1990),
  \item \verb"\citep{"\textit{key}\verb"}" produces citations in parentheses,
  e.g. (Jones et al. 1990),
  \item \verb"\citealt{"\textit{key}\verb"}" produces citations with no parentheses,
  e.g. Jones et al. 1990.
  \end{itemize}
For three-author papers, a full author list can be forced by
putting a \verb"*" just before the \verb"{". To add notes within
the citation, use the form
\verb"\citep["\textit{pre\_reference\_text}\verb"]["\textit{post\_reference\_text}\verb"]{"\textit{key}\verb"}"
(note that either of \textit{pre\_reference\_text} and
\textit{post\_reference\_text} can be blank).

Items in the reference list must be of the form\\
\verb"\bibitem[\protect\citeauthoryear{"\textit{author\_names}\verb"}{"\textit{year}\verb"}]{"\textit{key}\verb"}"
Text of reference ...\\
for one-, two- and multi-author papers, or\\
\verb"\bibitem[\protect\citeauthoryear{"\textit{three\_author\_names}\verb"}{"\textit{first\_author\_etal}\verb"}{"\textit{year}\verb"}]{"\textit{key}\verb"}"
Text of reference ...\\
for three-author papers.

Note that Patrick Daly's package \verb"natbib.sty" is required in
order to use the \verb"usenatbib" option.

We recommend that authors use \verb"natbib.sty" as their standard
cross-referencing package, because of the flexibility in citation style
that it provides.

\item \verb"usegraphicx" -- this loads the graphics package
\verb"graphicx.sty", which authors can use to include figures in
their papers. Note that the standard \LaTeX\
 graphics package \verb"graphicx.sty" is
 required in order to use the \verb"usegraphicx" option.
\end{enumerate}

Other style files, or packages providing features such as graphics
support, can be used in conjunction with \verb"mn.cls". To do
this, the command
\verb"\usepackage{"\textit{package\_name}\verb"}" is used.

An additional feature of the class file is that footnote symbols
are now in the correct journal style (symbols for title page
footnotes, superscript arabic numbers for text footnotes).

A BibTeX style file, \verb"mn2e.bst", is now available for
authors who wish to use BiBTeX. It is recommended that this
should be used in conjunction with \verb"natbib.sty".

For general instructions on preparing \textit{Monthly Notices} papers in
\LaTeX, please refer to the MNRAS \LaTeX style guide for authors,
available on the CTAN sites in subdirectory
\verb"/tex-archive/macros/latex209/mnras".

 \label{lastpage}


\end{document}
